Optimal updating factor in Wang-Landau and metadynamics simulations

### 2016-02-05 doc/invt.tex
reorganize the error code

Generally, for an arbitrary updating matrix $\mathbf w$,
direct optimization of Eq. \eqref{eq:error_asym1}
often leads to a complicated expression for $\alpha(t)$.
%
In practice, it is also useful to find
a simple expression for $\alpha(t)$
that is optimal with respect to some free parameter(s).
%
From Eq. \eqref{eq:alpha_opt},
a reasonable candidate would be
%
\begin{equation}
\alpha(\tau) = \frac{1}{\lambda \, (\tau + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
for some value of $\lambda$.
%
Below we shall assume this functional form
and find the optimal value
in some cases.
%
We shall show that the optimal $\lambda$
generally depends on not only the spectrum
of eigenvalues and the sampling method,
but also other parameters,
such as the simulation length, $t$.
%
Note, however,
since Eq. \eqref{eq:alpha_invtlambda}
does not fix the endpoint value,
%
\begin{equation}
q(t) = \frac{ 1 } { \lambda }
\log\left(
  \frac{ t + t_0 } { t_0 }
\right),
\label{eq:qt_invtlambda}
\end{equation}
%
we have to include the residual error
during the optimization.

>>>>

Generally, for an arbitrary updating matrix $\mathbf w$,
direct optimization of Eq. \eqref{eq:error_asym1}
often leads to a complicated expression for $\alpha(t)$.
%
In practice, it is also useful to find
a reasonably optimal $\alpha(t)$ with a simpler expression.
%
From Eq. \eqref{eq:alpha_opt},
we consider the following invert-time formula
%
\begin{equation}
\alpha(\tau) = \frac{1}{\lambda \, (\tau + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
for some value of $\lambda$.
%
Below we shall assume this functional form
and find the optimal value
in some cases.
%
We shall show that the optimal $\lambda$
generally depends on not only the spectrum
of eigenvalues and the sampling method,
but also other parameters,
such as the simulation length, $t$.
%
Note, however,
since Eq. \eqref{eq:alpha_invtlambda}
does not fix the endpoint value,
%
\begin{equation}
q(t) = \frac{ 1 } { \lambda }
\log\left(
  \frac{ t + t_0 } { t_0 }
\right),
\label{eq:qt_invtlambda}
\end{equation}
%
we have to include the residual error
during the optimization.
